19Q1

### 2019-04-16 19Q1.Rmd
rm celline_stack old file and updated 19Q1

@@

**Might not need this anymore due to increased care taken by DepMap to harmonize disease names**
```{r}
# ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
# lineage_converter <- unique(ccl_converter[, c("grouped_general_doid", "group_general_lineage_name")])
```

@@

DepMap 19Q1 update fixed almost all of the inconsistencies of the Primary.Disease column, though there were come capitalization inconsistencies.
```{r}
ccl_meta <- read.delim("./data_munging/19Q1/DepMap-2019q1-celllines_v2_20190305.csv", sep = ",", header = TRUE, na.strings = c("", NA))
ccl_meta$Primary.Disease <- tolower(ccl_meta$Primary.Disease)
ccl_meta <- subset(ccl_meta, Primary.Disease != "unknown" & Primary.Disease != "primary cells" & !grepl("MERGED", CCLE_Name, fixed = TRUE))
ccl_meta$Cell_line <- as.character(lapply(ccl_meta$CCLE_Name, function(x) strsplit(as.character(x), split = "_")[[1]][1]))
ccl_meta$histology <- tolower(gsub("^[a-z0-9]*_", "", ccl_meta$CCLE_Name, ignore.case = TRUE))
# Convert Primary.Disease entries to all lower case to fix factorization issue
ccl_meta$Primary.Disease <- as.factor(tolower(ccl_meta$Primary.Disease))
# Harmonize ID column name and rename CCLE_Name column to fit with dataframe style
colnames(ccl_meta)[colnames(ccl_meta) == "CCLE_Name"] <- "CCLE_ccl_name"
colnames(ccl_meta)[colnames(ccl_meta) == "DepMap_ID"] <- "Broad_ID"
```

@@

# Order and genes taken from pink heatmapo from Daniel's analyses
g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
```

```{r}
# levels(g2p_filt$Phenotype.Description)
unique(g2p_filt$group_general_lineage_name)
levels(g2p_filt$group_general_lineage_name)

@@

>>>>

```{r functions}
unfactorize <- function(df){
  for(i in which(sapply(df, class) == "factor")) {
    df[[i]] = as.character(df[[i]])
  }
  return(df)
}
```

@@

**Might not need this anymore due to increased care taken by DepMap to harmonize disease names**
```{r}
ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
lineage_converter <- unique(ccl_converter[, c("Broad_ID", "grouped_general_doid", "group_general_lineage_name")])
```

@@

DepMap 19Q1 update fixed almost all of the inconsistencies of the Primary.Disease column, though there were come capitalization inconsistencies.
```{r}
ccl_meta <- read.delim("./data_munging/19Q1/DepMap-2019q1-celllines_v2_20190305.csv", sep = ",", header = TRUE, na.strings = c("", NA))
ccl_meta$Primary.Disease <- tolower(ccl_meta$Primary.Disease)
ccl_meta <- subset(ccl_meta, Primary.Disease != "unknown" & Primary.Disease != "primary cells" & !grepl("MERGED", CCLE_Name, fixed = TRUE))
ccl_meta$Cell_line <- as.character(lapply(ccl_meta$CCLE_Name, function(x) strsplit(as.character(x), split = "_")[[1]][1]))
ccl_meta$histology <- tolower(gsub("^[a-z0-9]*_", "", ccl_meta$CCLE_Name, ignore.case = TRUE))
# Convert Primary.Disease entries to all lower case to fix factorization issue
ccl_meta$Primary.Disease <- as.factor(tolower(ccl_meta$Primary.Disease))
# Harmonize ID column name
colnames(ccl_meta)[colnames(ccl_meta) == "DepMap_ID"] <- "Broad_ID"

# Remove two rows that contain cell lines with two different histologies
# The histologies that are kept are verified through matching in Cellosaurus and Cell Model Passports
# KMH2, haematopoietic_and_lymphoid: https://web.expasy.org/cellosaurus/CVCL_1330, https://cellmodelpassports.sanger.ac.uk/passports/SIDM01018
# MS1, lung: https://web.expasy.org/cellosaurus/CVCL_1429, https://cellmodelpassports.sanger.ac.uk/passports/SIDM00245
ccl_meta <- subset(ccl_meta, CCLE_Name != "KMH2_THYROID" & CCLE_Name != "MS1_SKIN")
```

@@

# Order and genes taken from pink heatmap from Daniel's analyses
# g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
```

```{r, eval=FALSE}
# levels(g2p_filt$Phenotype.Description)
unique(g2p_filt$group_general_lineage_name)
levels(g2p_filt$group_general_lineage_name)

@@

**UPDATE WITH POZDEYEV AUC DATA**

```{r}
ccle <- read.delim("./../htscreens_giant_files/pozdeyev_data/CCLE_drug_response_metrics.csv.gz", sep = ",")
ctrp <- read.delim("./../htscreens_giant_files/pozdeyev_data/CTRP_drug_response_metrics.csv.gz", sep = ",")
gdsc <- read.delim("./../htscreens_giant_files/pozdeyev_data/GDSC_drug_response_metrics.csv.gz", sep = ",")
```
